Nitric oxide feedback to ciliary photoreceptor cells gates a UV avoidance circuit

### 2023-06-14 Manuscript/Manuscript.Rmd
Acknowledge

This work was funded by the Wellcome Trust (214337/Z/18/Z).
This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 101020792).
KJ has been supported by a JSPS Postdoctoral fellowhip, LAYG by a BBSRC Discovery fellowship (BB/W010305/1), PS by a Wellcome Trust Institutional Strategic Support Award (204909/Z/16/Z), and KCAW by the EPSRC Hub for Quantitive Modelling in Healthcare (EP/T017856/1).

>>>>

This work was funded by the Wellcome Trust (214337/Z/18/Z).
This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 101020792).
KJ has been supported by a JSPS Overseas Research Fellowship, LAYG by a BBSRC Discovery fellowship (BB/W010305/1), PS by a Wellcome Trust Institutional Strategic Support Award (204909/Z/16/Z), and KCAW by the EPSRC Hub for Quantitive Modelling in Healthcare (EP/T017856/1).
